Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph\tnoteref{t1,t2}

### 2016-04-22 curvature.tex
match color scheme to figures

	\caption{\
        Distribution of rSPR $\MH$ access times (x-axis) for all pairs of 5-taxon trees, grouped by the degree of the trees.
        Color signifies rSPR distance between the trees, with green, orange, blue, light blue, and brown signifying distances of 1, 2, 3, 4, and 5, respectively; the saturation of the color shows coarse curvature $\curvature{\MH; \cdot, \cdot}$, such that increased saturation (i.e.\ darker color) indicates a smaller $\kappa$.
	}
	\label{fig:kappa-access-distribution}
\end{figure*}

@@

	\hspace*{\stretch{1}}
	\subfigure[\label{fig:5t-long-time-kappa-access}]{\includegraphics[width=2.3in]{figs/5t-long-time-kappa-access}}
	\hspace*{\stretch{2}}
	\subfigure[\label{fig:6t-long-time-kappa-access}]{\includegraphics[width=2.3in]{figs/6t-long-time-kappa-access}}
	\hspace*{\stretch{1}}
    \caption{\
        Distribution of early rSPR $\MH$ access times for those pairs of (a) 6-taxon trees with degree 44 and (b) 7-taxon trees with degree 70.
        Distribution of later rSPR $\MH$ access times for those pairs of (c) 5-taxon trees with degree 24 and (d) 6-taxon trees with degree 44.
				In both cases we exclude pairs that are simple inclusions of pairs of trees with a smaller number of taxa.
				Color signifies rSPR distance between the trees, with green, orange, and blue signifying distances of 1, 2, and 3, respectively; the saturation of the color shows coarse curvature $\curvature{\MH; \cdot, \cdot}$, such that increased saturation (i.e.\ darker color) indicates a smaller $\kappa$.
        }
	\label{fig:kappa-access}
\end{figure*}

>>>>

	\caption{\
        Distribution of rSPR $\MH$ access times (x-axis) for all pairs of 5-taxon trees, grouped by the degree of the trees.
				Color signifies rSPR distance between the trees, with green, orange, and blue signifying distances of 1, 2, and 3, respectively; the saturation of the color shows coarse curvature $\curvature{\MH; \cdot, \cdot}$, such that increased saturation (i.e.\ darker color) indicates a smaller $\kappa$.
	}
	\label{fig:kappa-access-distribution}
\end{figure*}

@@

	\hspace*{\stretch{1}}
	\subfigure[\label{fig:5t-long-time-kappa-access}]{\includegraphics[width=2.3in]{figs/5t-long-time-kappa-access}}
	\hspace*{\stretch{2}}
	\subfigure[\label{fig:6t-long-time-kappa-access}]{\includegraphics[width=2.3in]{figs/6t-long-time-kappa-access}}
	\hspace*{\stretch{1}}
    \caption{\
        Distribution of early rSPR $\MH$ access times for those pairs of (a) 6-taxon trees with degree 44 and (b) 7-taxon trees with degree 70.
        Distribution of later rSPR $\MH$ access times for those pairs of (c) 5-taxon trees with degree 24 and (d) 6-taxon trees with degree 44.
				In both cases we exclude pairs that are simple inclusions of pairs of trees with a smaller number of taxa.
        Color signifies rSPR distance between the trees, with green, orange, blue, and light blue signifying distances of 1, 2, 3, and 4, respectively; the saturation of the color shows coarse curvature $\curvature{\MH; \cdot, \cdot}$, such that increased saturation (i.e.\ darker color) indicates a smaller $\kappa$.
        }
	\label{fig:kappa-access}
\end{figure*}
